Reproduction of Civic Honesty around the Globe

### 2021-03-24 outputs/paper/paper.Rmd
Fix typos

---
title: "Reproduction of Civic Honesty around the Globe"
subtitle: "Are the chosen 40 countries representative of the world?"
author: "Bongju Yoo and Najma Osman"
thanks: "Code and data are available at: https://github.com/bonjwow/lost-wallet"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "By reproducing the research paper, Civic honesty around the globe, we examined what sampling methods the authors chose and how the data was gathered, and verified the regression models used in the original paper. We discovered that some of the variables in the original dataset contained the data collector’s estimation and judgment, and the rationale for selecting the countries was weak and unclear. The original research paper can be extended and/or improved with right choices of nations, more concrete criteria to measure abstract concepts, and considerations of socioeconomic status of the areas."
output:
  bookdown::pdf_document2:
header-includes:
   - \usepackage{dcolumn} 
toc: FALSE
bibliography: references.bib
---

@@

Firstly, we looked into the original dataset and examined what sampling approach the research team used and how the data was collected. We found that some of the variables in the dataset were recorded highly based on the research assistant's estimation and judgment since they had to measure abstract concepts such as actions and behaviors. Also, we found that the rationale for selecting the countries was ambiguous. These inaccurate and unclear methods of collecting the data can lead to lower the reliability and validity of the results of the research. Additionally, we ran power analysis to verify whether or not the sample sizes used in the dataset were appropriate and confirmed that the sizes were large enough to detect a statistically significant difference between the control group and treatment group. Secondly, we identified which independent variables impact the most significant influence on dependent variables, using ordinary least squares (OLS) regression. The results of our regression models were slightly different from the original ones: the absence or presence of coworker/coworkers was statistically significant; otherwise, being ages 40+ was not statistically significant. However, in general, most of the results were the same as the original paper.

@@

## Description of Dataset
This type of the dataset is a csv file, it is imported from the Harvard Dataverse Repository and uploaded June 15th, 2019 [@citeDataverse]. There were 57 variables and 17,303 observations, but we selected 12 variables using the `R` programming language [@citeR] and the `tidyverse` package [@citeTidyverse]. The selected variables are: id, country (unique numeric code for each country), Country (the name of the country), city, institution (drop-off locations), cond (no money, money, and big money conditions), response (reported or not), age, above40 (the estimated age of the recipient), male (the gender of the recipient), coworkers, computer, other_bystanders. All of those attributes are coded as numerical values except for Country, which is code as alphabetical values. The key variables are response, country, cond, and response: the response variable was used as a dependent variable, the no money condition was used as a control variable, and the other two conditions were used as treatments.

@@

These situational factors were recorded by research assistants, and some of the factors highly rely on their individual judgment. For example, the ‘Busyness’ category, which is measured on a 7-point scale from “not at all” (0) to “very busy”, and the ‘Friendliness’ category, which is measured on a 7-point scale from “very unfriendly” (0) to “very friendly” (6), were graded by the assistants according to their estimation and judgment since they had to measure actions and behaviors which are intangible unlike a computer or security camera [@citeCohn].

In addition, the estimation of the assistants can be incorrect, and eventually they might record false information during the data collection process. For example, in terms of the ‘Recipient age’ category, the assistants had to guess the recipient’s age and select one from six options: < 20, 20-30, 30-40, 40-50, 50-60, and > 60. What if the recipient looks 30? The assistants might choose either 20-30 or 30-40 based on their judgment since it is a huge challenge to correctly guess someone's age by looking at his or her face. A research team from the Department of Computer Science and Engineering at Michigan State University studied the ability of humans to estimate age using face images collected from crowdsourcing and found that the accuracy of guessing the age correctly with a margin of error of plus/minus 5 years is between 50% and 70% [@citeAgeEstimation]. Namely, there are high chances that the assistants might have recorded inaccurate information for some of those variables that require the researcher's estimation. As a consequence, this can lead to distorted results of the analysis.

Figure \@ref(fig:figReportedByCountry) is a replica of the dumbbell plot included in the original research paper, which shows share of returned (reported) wallets in NoMoney and Money conditions by country. And, Figure \@ref(fig:figMonetaryStakes) is a replica of the line plot included in the paper, which showsshare of returned (reported) wallets in the three conditions; NoMoeny, Money, and BigMoney. We filtered the raw dataset using the `dplyr` package [@citeDplyr] and display the data in a dumbbell plot and line plot using the `ggplot` [@citeGgplot2]. As can be seen in the figures, people were more likely to return wallets with more money in most of the countries selected for the research, and the reporting rate increases if wallets contain bigger money. If so, can we say that people tend to return wallets contained bigger money in "most countries"?

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = colorGray,
                colour_x = colorOrange, 
                colour_xend = colorRed,
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue")) +
  theme(panel.grid.major.x = element_line(size = 0.02))

@@

## Power Analysis
We ran power analysis to check whether the research team used an appropriate sample size for the original paper. Firstly, we calculated the proportions of the returned wallets in the control group (the ‘no money’ condition) and the treatment group (‘the ‘money’ condition), using the raw data using the `dplyr`’s select, group_by, summarise, and mutate functions [@citeDplyr]. Then, we calculated the effect size, using the formula written by Stephane Champely [@citePwrPdf]. Lastly, we ran the two-sample test for proportions to estimate the required sample size which is required to show a significant difference between the two groups, using the `pwr` package [@citePwr]. The result of the test shows that the most appropriate size of a sample to compare the two condition groups is 313 for each. Since the sample size of the control group is 7,888 and that of the treatment group is 8,211, we can say that the sample size is large enough to find a statistically significant difference between the two groups. The result of the power analysis is displayed below.

@@

# Model
We used a linear regression model, specifically ordinary least squares (OLS), which are used to examine relationships between variables, specifically looking to determine which independent variables hold the most and/or significant influence over dependent variables - in this case, whether the wallet is reported or not. In addition to this, we can see how changes in the independent variables are related to changes in the dependent variable through use of dummy variables. It allows us to understand the mean change in a dependent variable, given a 1 unit change in each independent variable.Three regressions were run. Table 1’s second column and Table 2 consists of multiple linear regressions, Table 1’s first column and Table 3 are simple linear regressions.

@@

* No heteroscedasticity: the error term has a constant variance,
* Linearity in Parameters: the regression model is linear in coefficients and error term,
* Zero conditional mean: error term has a population mean of zero 
* Variation in X: there is variation in the explanatory variable,
* Normality - No IV is a perfect linear function of other explanatory variables,
* And Random Sampling: the observed data represents a random sample from the population

@@

To run the OLS model, we used the @citeR inbuilt function, lm(), which is used to fit linear models. It has two key arguments: formula, and data. Formula takes on the form y ~ x1 + x2, where y is the dependent variable and x1, x2, and onward are the independent variable, while data is the data frame containing the columns specified in the formula. The stargazer package by @citeStargazer was used to create the LaTeX regression tables.

@@

Table 1’s results are aggregated across the 40 countries visited to conduct the experiment. Results show the following:
* Lost wallet reporting rates increase by 12 percentage points in the Money relative to the NoMoney condition
* Men are less likely to report a wallet than woman 
the presence of a computer increased likelihood of reporting the lost wallet,
* but the presence of other bystanders decreased reporting rates,
* However, unlike in the original paper, age groups (above and under 40), and the presence of coworkers had no statistical significance regarding reporting or failing to report lost wallets.

@@

Table 2 examines reporting rates for the Money and BigMoney conditions in the UK, Poland, and the USA.
* Column 1 shows that across the three countries, they were more likely to report a lost wallet containing greater amounts of money.
* Columns 2-4, where the countries are isolated, shows a trend that wallets with larger amounts of money are more likely to be reported.
* With smaller amounts of money, only the UK and US showed statistically significant likelihood of reporting the lost wallets.

>>>>

---
title: "Reproduction of Civic Honesty around the Globe"
subtitle: "Are the chosen 40 countries representative of the world?"
author: "Bongju Yoo and Najma Osman"
thanks: "Code and data are available at: https://github.com/bonjwow/lost-wallet"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "By reproducing the research paper, Civic honesty around the globe, we examined what sampling methods the authors chose and how the data was gathered, and verified the regression models used in the original paper. We discovered that some of the variables in the original dataset heavily relied on the data collector’s estimation and judgment, and the rationale for selecting the countries was weak and unclear. The original research paper can be extended and/or improved with right choices of nations, more concrete criteria to measure abstract concepts, and considerations of socioeconomic status of the areas."
output:
  bookdown::pdf_document2:
header-includes:
   - \usepackage{dcolumn} 
toc: FALSE
bibliography: references.bib
---

@@

Firstly, we looked into the original dataset and examined what sampling approach the research team used and how the data was collected. We found that some of the variables in the dataset were recorded highly based on the research assistant's estimation and judgment since they had to measure abstract concepts such as actions and behaviors. Also, we discovered that the rationale for selecting the countries was ambiguous. These inaccurate and unclear methods of collecting the data can lead to lower the reliability and validity of the results of the research. Additionally, we ran power analysis to verify whether or not the sample sizes used in the dataset were appropriate and confirmed that the sizes were large enough to detect a statistically significant difference between the control group and treatment group. Secondly, we identified which independent variables impact the most significant influence on dependent variables, using ordinary least squares (OLS) regression. The results of our regression models were slightly different from the original ones: the absence or presence of coworker/coworkers was statistically significant; otherwise, being ages 40+ was not statistically significant. However, in general, most of the results were the same as the original paper.

@@

## Description of Dataset
This type of the dataset is a csv file, it is imported from the Harvard Dataverse Repository and uploaded June 15th, 2019 [@citeDataverse]. There were 57 variables and 17,303 observations, but we selected 12 variables using the `R` programming language [@citeR] and the `tidyverse` package [@citeTidyverse]. The selected variables are: id, country (unique numeric code for each country), Country (the name of the country), city, institution (drop-off locations), cond (no money, money, and big money conditions), response (reported or not), age, above40 (the estimated age of the recipient), male (the gender of the recipient), coworkers, computer, other_bystanders. All of those attributes are coded as numerical values except for Country, which is coded as alphabetical values. The key variables are response, country, cond, and response: the response attribute was used as a dependent variable; the no money condition was used as a control variable; and the other two conditions were used as treatments for the regression model.

@@

These situational factors were recorded by research assistants, and some of the factors highly relied on their individual judgment. For example, the ‘Busyness’ category, which was measured on a 7-point scale from “not at all” (0) to “very busy”, and the ‘Friendliness’ category, which was measured on a 7-point scale from “very unfriendly” (0) to “very friendly” (6), were graded by the assistants according to their estimation and judgment since they had to measure actions and behaviors which are intangible unlike a computer or security camera [@citeCohn].

In addition, the estimation of the assistants can be incorrect, and eventually they might record false information during the data collection process. For example, in terms of the ‘Recipient age’ category, the assistants had to guess the recipient’s age and select one from six options: < 20, 20-30, 30-40, 40-50, 50-60, and > 60. What if the recipient looks 30? The assistants might choose either 20-30 or 30-40 based on their judgment since it is a huge challenge to correctly guess someone's age by looking at his or her face. A research team from the Department of Computer Science and Engineering at Michigan State University studied the ability of humans to estimate age using face images collected from crowdsourcing and found that the accuracy of guessing the age correctly with a margin of error of plus/minus 5 years is between 50% and 70% [@citeAgeEstimation]. Namely, there were high chances that the assistants might have recorded inaccurate information for some of those variables that require the assistant's estimation. As a consequence, this can lead to distorted results of the analysis.

Figure \@ref(fig:figReportedByCountry) is a replica of the dumbbell plot included in the original research paper, which shows share of returned (reported) wallets in NoMoney and Money conditions by country. And, Figure \@ref(fig:figMonetaryStakes) is a replica of the line plot included in the paper, which shows share of returned (reported) wallets in the three conditions; NoMoeny, Money, and BigMoney. We filtered the raw dataset using the `dplyr` package [@citeDplyr] and displayed the data in a dumbbell plot and line plot using the `ggplot` package [@citeGgplot2]. As can be seen in the figures, people were more likely to return wallets with more money in most of the countries selected for the research, and the reporting rate increased if wallets contained bigger money. If so, can we say that people tend to return wallets contained bigger money in "most countries"?

@@

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = colorGray,
                colour_x = colorOrange, 
                colour_xend = colorRed,
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
  labs(x = NULL, y = NULL, title = "") +
  theme_minimal() +
  theme(panel.grid.major.x = element_line(size = 0.02),
        legend.position = "top")

@@

## Power Analysis
We ran power analysis to check whether the research team used an appropriate sample size for the original paper. Firstly, we calculated the proportions of the returned wallets in the control group (the ‘no money’ condition) and the treatment group (‘the ‘money’ condition), using the raw data using the `dplyr`’s select, group_by, summarise, and mutate functions [@citeDplyr]. Then, we calculated the effect size, using the formula written by Stephane Champely [@citePwrPdf]. Lastly, we ran the two-sample test for proportions to estimate the required sample size which is required to show a significant difference between the two groups, using the `pwr` package [@citePwr]. The result of the test shows that the most appropriate size of a sample to compare the two condition groups is 313 for each. Since the sample size of the control group is 7,888 and that of the treatment group is 8,211, we can say that the sample size was large enough to find a statistically significant difference between the two groups. The result of the power analysis is displayed below.

@@

# Model
We used a linear regression model, specifically ordinary least squares (OLS), which are used to examine relationships between variables, specifically looking to determine which independent variables hold the most and/or significant influence over dependent variables - in this case, whether the wallet is reported or not. In addition to this, we can see how changes in the independent variables are related to changes in the dependent variable through use of dummy variables. It allows us to understand the mean change in a dependent variable, given a 1 unit change in each independent variable. In total, three regressions were run. Table 1’s second column and Table 2 consists of multiple linear regressions, Table 1’s first column and Table 3 are simple linear regressions.

@@

* No heteroscedasticity: the error term has a constant variance,
* Linearity in Parameters: the regression model is linear in coefficients and error term,
* Zero conditional mean: error term has a population mean of zero, 
* Variation in X: there is variation in the explanatory variable,
* Normality - No IV is a perfect linear function of other explanatory variables,
* And, Random Sampling: the observed data represents a random sample from the population

@@

To run the OLS model, we used the @citeR inbuilt function, lm(), which is used to fit linear models. It has two key arguments: formula, and data. Formula takes on the form y ~ x1 + x2, where y is the dependent variable and x1, x2, and onward are the independent variable, while data is the data frame containing the columns specified in the formula. The `stargazer` package by @citeStargazer was used to create the LaTeX regression tables.

@@

Table 1’s results are aggregated across the 40 countries visited to conduct the experiment. Results show the following:

* Lost wallet reporting rates increase by 12 percentage points in the Money relative to the NoMoney condition
* Men are less likely to report a wallet than woman 
the presence of a computer increased likelihood of reporting the lost wallet,
* but the presence of other bystanders decreased reporting rates,
* However, unlike in the original paper, age groups (above and under 40), and the presence of coworkers had no statistical significance regarding reporting or failing to report lost wallets.

@@

Table 2 examines reporting rates for the Money and BigMoney conditions in the UK, Poland, and the USA.

* Column 1 shows that across the three countries, they were more likely to report a lost wallet containing greater amounts of money.
* Columns 2-4, where the countries are isolated, shows a trend that wallets with larger amounts of money are more likely to be reported.
* With smaller amounts of money, only the UK and US showed statistically significant likelihood of reporting the lost wallets.
